Discrete Quantum Theories and Computing

### 2019-04-26 dissertation.tex
dissertation.lyx Adding protected space between URL and period...

\begin{preface*}
\begin{itemize}
\item The latest PDF version of this thesis is in GitHub: \url{https://git.io/fxbuG}.
\item Its source code is typeset using \LyX{} \cite{LyX} in \url{https://git.io/fxbuE}
and the exported \LaTeX{} file is in \url{https://git.io/fhZBW}.
\item Any comments can be left in the Issue part of the GitHub repository:
\url{https://git.io/fxbug}.
\end{itemize}
Following explains how to compile the PDF from the \LaTeX{} source:
\begin{enumerate}
\item \label{enu:Clone-the-git}Clone the git repository of this thesis
\url{https://git.io/fhZP5} into your local directory and the thesis
document class \url{https://github.com/yuttai/iuphd} in a location
where the system can find.
\item In the local directory of this thesis, run \code{xelatex dissertation.tex}.
\item Run \code{biber dissertation}.
\item Run \code{xelatex dissertation.tex} several times until all the references
are resolved.
\end{enumerate}
The previous steps only tested in Microsoft Windows with MiK\TeX{}
2.9. Please report me if there is any difficulty to compile it. Besides,
to compile a PDF file from the \LyX{} source, just finish step~\ref{enu:Clone-the-git},
open \code{dissertation.lyx} in \LyX , and click the toolbar button
\includegraphics[width=1em]{buffer-view}.\end{preface*}

@@

After defining a QPMFF~$\mu$, we would like to follow the idea of
Gleason's theorem to see whether we might trace back from $\mu$ to
a pure or mixed state and summarize this correspondence as a discrete
Born rule. When $p=D=3$, there is indeed some correspondence between
QPMFFs and states. However, when $D=3$ and $p=7$, we have numerically
verified that the unique QPMFF $\mu\colon\events_{7^{2}}\rightarrow\left[0,1\right]$
is the equal probable one
\begin{equation}
\mu\left(P\right)=\begin{cases}
0 & \textrm{if }P=\mathbb{0}\,;\\
\frac{1}{3} & \textrm{if }P\textrm{ is a one-dimen\-sional projector;}\\
\frac{2}{3} & \textrm{if }P\textrm{ is a two-dimen\-sional projector;}\\
1 & \textrm{if }P=\mathbb{1}\,.
\end{cases}\label{eq:QPMFF37}
\end{equation}
However, the irreducible pure states in $\ff{7^{2}}^{3}$ is not unique.
Indeed, there are 
\begin{equation}
\frac{7^{3-1}\left(7^{3}-\left(-1\right)^{3}\right)}{7+1}=2107\label{eq:numberOfIrreducibleStates-7-3}
\end{equation}
irreducible pure states in $\ff{7^{2}}^{3}$ as we computed in Eq.~(\ref{eq:numberOfIrreducibleStates}).
Since we don't have enough QPMFF to correspond even pure states, there
is no discrete Born rule in this case. In general, we conjecture that
QPMFF is always unique for $D\ge3$ except $D=p=3$.

>>>>

\begin{preface*}
\begin{itemize}
\item The latest PDF version of this thesis is in GitHub: \url{https://git.io/fxbuG}~.
\item Its source code is typeset using \LyX{} \cite{LyX} in \url{https://git.io/fxbuE}
and the exported \LaTeX{} file is in \url{https://git.io/fhZBW}~.
\item Any comments can be left in the Issue part of the GitHub repository:
\url{https://git.io/fxbug}~.
\end{itemize}
Following explains how to compile the PDF from the \LaTeX{} source:
\begin{enumerate}
\item \label{enu:Clone-the-git}Clone the git repository of this thesis
\url{https://git.io/fhZP5} into your local directory and the thesis
document class \url{https://github.com/yuttai/iuphd} in a location
where the system can find.
\item In the local directory of this thesis, run \code{xelatex dissertation.tex}~.
\item Run \code{biber dissertation}~.
\item Run \code{xelatex dissertation.tex} several times until all the references
are resolved.
\end{enumerate}
The previous steps only tested in Microsoft Windows with MiK\TeX{}
2.9. Please report me if there is any difficulty to compile it. Besides,
to compile a PDF file from the \LyX{} source, just finish step~\ref{enu:Clone-the-git},
open \code{dissertation.lyx} in \LyX , and click the toolbar button
\includegraphics[width=1em]{buffer-view}.\end{preface*}

@@

After defining a QPMFF~$\mu$, we would like to follow the idea of
Gleason's theorem to see whether we might trace back from $\mu$ to
a pure or mixed state and summarize this correspondence as a discrete
Born rule. When $p=D=3$, there is indeed some correspondence between
QPMFFs and states. However, when $D=3$ and $p=7$, we have numerically
verified that the unique QPMFF $\mu\colon\events_{7^{2}}\rightarrow\left[0,1\right]$
is the equal probable one
\begin{equation}
\mu\left(P\right)=\begin{cases}
0 & \textrm{if }P=\mathbb{0}\,;\\
\frac{1}{3} & \textrm{if }P\textrm{ is a one-dimen­sional projector;}\\
\frac{2}{3} & \textrm{if }P\textrm{ is a two-dimen­sional projector;}\\
1 & \textrm{if }P=\mathbb{1}\,.
\end{cases}\label{eq:QPMFF37}
\end{equation}
However, the irreducible pure states in $\ff{7^{2}}^{3}$ is not unique.
Indeed, there are 
\begin{equation}
\frac{7^{3-1}\left(7^{3}-\left(-1\right)^{3}\right)}{7+1}=2107\label{eq:numberOfIrreducibleStates-7-3}
\end{equation}
irreducible pure states in $\ff{7^{2}}^{3}$ as we computed in Eq.~(\ref{eq:numberOfIrreducibleStates}).
Since we don't have enough QPMFF to correspond even pure states, there
is no discrete Born rule in this case. In general, we conjecture that
QPMFF is always unique for $D\ge3$ except $D=p=3$.
